\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-24 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
relecture OA Lise fin

This estimation method also implies a lower coverage, both in time and in the sectors/countries covered. With respect to time coverage, information about the port of entry is only available since 1989, which is already smaller than our full sample starting in 1974. On top of that, because of the Covid situation, the US Bureau of Census was only able to provide us the data for the years 1997-1999 and 2001-2019. Using it would hence reduce the time coverage of our analysis by more than 20 years (skipping the 1974-1996 years in particular). In our view, the historical coverage is interesting \emph{per se}: it provides useful insights about how transport costs have evolved over several decades and more importantly, it allows us to highlight the welfare alterations induced over the ``hyper-globalization" period by the relative dynamics of additive and multiplicative costs.

@@

\textbf{XXX Lise stop here relecture XXX }
\subsubsection{Weights and quantities}

@@

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions strongly limit both the number of sectors and of countries covered, and do also impact the value of trade flows covered. This raises a non-trivial sample selection bias that may reduce the general scope of the transport cost estimates. Second, in terms of $\beta$ estimates, the results clearly show that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air). In this respect, they stand in line with the results of \cite{Lashkaripour_JIE2020}, and confirm the correlation between weight per unit and unit price. Still, the share of additive cost is not reduced to zero (except if one looks at the median for vessel). Thus these results do not disqualify our approach, especially as we cover a much larger period and sample with our baseline estimate.

@@

Another argument is illustrated by Figure \ref{graph_Share_of_discrete_goods.png}. After computing the share of discrete goods per 5-digit SITC import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports on a yearly basis. According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, reaching a value only above 50\% for two years. Switching to a per-unit approach would hence mean a marked reduction in the trade flows coverage, thereby limiting the general scope of our estimates.

@@

The situation is similar in the primary sector. In this case, in air transport te composition effect matters more (Figure \ref{fig:totalTC_compeffects_excl_primary}, left-hand panels (a), (b) and (c)), while we observe not much role for them in vessel transport (Figure \ref{fig:totalTC_compeffects_excl_primary}, right-hand panels (d), (e) and (f)).

>>>>

This estimation method also implies a lower coverage, both in time and in the sectors/countries covered. With respect to time coverage, information about the port of entry is only available since 1989, which is already smaller than our full sample starting in 1974. On top of that, because of the Covid situation, the US Bureau of Census was only able to provide us the data for the years 1997-1999 and 2001-2019. Using it would hence reduce the time coverage of our analysis by more than 20 years (skipping the 1974-1996 years in particular). In our view, the historical coverage is interesting \emph{per se}: it provides useful insights about how transport costs have evolved over several decades and more importantly, it allows us to highlight the welfare alterations induced over the ``hyper-globalization'' period by the relative dynamics of additive and multiplicative costs.

@@

\subsubsection{Weights and quantities}

@@

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions strongly limit both the number of sectors and of countries covered, and do also impact the value of trade flows covered.
A related argument is illustrated by Figure \ref{graph_Share_of_discrete_goods.png}. After computing the share of discrete goods per 5-digit SITC import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports on a yearly basis. According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, reaching a value only above 50\% for two years. Switching to a per-unit approach would hence mean a marked reduction in the trade flows coverage, thereby limiting the general scope of our estimates.

Second, in terms of $\beta$ estimates, the results clearly show that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air). In this respect, they stand in line with the results of \cite{Lashkaripour_JIE2020}, and confirm the correlation between weight per unit and unit price. Still, the share of additive cost is not reduced to zero (except if one looks at the median for vessel). Thus these results do not disqualify our approach, especially as we cover a much larger period and sample with our baseline estimate.

@@

@@

The situation is different in the primary sector. In this case, in air transport the composition effects matter more (Figure \ref{fig:totalTC_compeffects_excl_primary}, left-hand panels (a), (b) and (c)), while we observe not much role for them in vessel transport (Figure \ref{fig:totalTC_compeffects_excl_primary}, right-hand panels (d), (e) and (f)).
